Capstone Movielens Report

### 2025-12-11 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions' description: `train_UMGY_SmoothedDay_effect`, `train_UMGY_SmoothedDay_effect.cv`.

Internally, this function calls the helper functions [calc_day_general_effect](#func.calc_day_general_effect) and [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) (both described above in this section), passing the values of the arguments [degree](#func.calc_UMGY_SmoothedDay_effect.args.degree) and [span](#func.calc_UMGY_SmoothedDay_effect.args.span) to the latter function in the same-named arguments.

@@

Under the hood, this function internally calls the [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) functions (both described above in this section).

>>>>

Internally, this function calls the helper functions [calc_day_general_effect](#func.calc_day_general_effect) and [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) (both described above in this section), passing the values of the arguments [degree](#func.train_UMGY_SmoothedDay_effect.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.args.span) to the latter function in the same-named arguments.

@@

Internally, this function calls the auxiliary functions [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) (both described above in this section), passing the values of the arguments [degree](#func.train_UMGY_SmoothedDay_effect.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.args.span) to the latter function in the same-named arguments..
